\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{cite}
\usepackage[pdftex, bookmarks=true]{hyperref}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usepackage{pgfplots}
\usepgfplotslibrary{groupplots}
\usepackage[margin=0.75in]{geometry}

% Make a draft watermark.
% \usepackage{draftwatermark}
% \SetWatermarkFontSize{40pt}
% \SetWatermarkScale{4.0}

% TODO: Use bibtex or some better bibliography management
% tool.

\input{style.tex}
\input{macros.tex}

\begin{document}

\title{\textbf{\Large A Standard \code{flat_map}}}
\date{}
{\let\newpage\relax\maketitle}

\noindent\textbf{Document Number:} D0429R3\\
\textbf{Date:} 2016-08-31\\
\textbf{Reply to:} Zach Laine whatwasthataddress@gmail.com\\
\textbf{Audience:} LWG/LEWG

\section{Revisions}

\label{sec:revisions}

\subsection{Changes from R2}

\begin{itemize}
  \item \code{value_type} is now \code{pair<const Key, T>}.
  \item \code{ordered_unique_sequence_tag} is now \code{sorted_unique_t}, and
    is applied uniformly such that those overloads that have it are assumed to
    receive sorted input, and those that do not have it are not.
  \item The overloads taking two allocators now take only one.
  \item \code{extract()} now returns a custom type instead of a \code{pair}.
  \item Add \code{contains()} (tracking \code{map}).
\end{itemize}

\subsection{Changes from R1}

\begin{itemize}
  \item Add deduction guides.
  \item Change \code{value_type} and reference types to be proxies, and remove
    \code{\{const_\},pointer}.
  \item Split storage of keys and values.
  \item Pass several constructor parameters by value to reduce the number of overloads.
  \item Remove the benchmark charts.
\end{itemize}

\subsection{Changes from R0}

\begin{itemize}
  \item Drop the requirement on container contiguity; sequence container will
    do.
  \item Remove \code{capacity()}, \code{reserve()}, and \code{shrik_to_fit()}
    from container requirements and from \code{flat_map} API.
  \item Drop redundant implementation variants from charts.
  \item Drop erase operation charts.
  \item Use more recent compilers for comparisons.
  \item Add analysis of separated key and value storage.
\end{itemize}

\section{Introduction}

\label{sec:intro}

This paper outlines what a (mostly) API-compatible, non-node-based \code{map}
might look like.  Rather than presenting a final design, this paper is
intended as a starting point for discussion and as a basis for future work.
Specifically, there is no mention of \code{multimap}, \code{set}, or
\code{multiset}.  Those will be added in later papers.

\input{motivation_and_scope}
\input{proposed_design}

\end{document}
